\section{Encoding map}
\label{sec:encoding_map}

The objective of this paper is not to propose a model of particle masses or mixing, but to define a
\emph{deterministic and auditable encoding} that maps measured observables into a discrete
representation suitable for bounded scans and reproducible diagnostics.
This section specifies that encoding in full, independent of any subsequent fitting or interpretation.

\subsection{Domain and codomain}

Let $x$ denote a positive-valued physical observable (e.g.\ a fermion mass or mixing-related input)
expressed in fixed physical units.
The encoding map is a function
\begin{equation}
\mathcal{E} : x \;\mapsto\; \Delta(x),
\end{equation}
where $\Delta(x)$ is a real-valued coordinate in logarithmic space defined relative to a chosen anchor
(Section~\ref{sec:anchoring_conventions}).

The codomain of $\mathcal{E}$ is $\mathbb{R}$, but all subsequent analyses restrict attention to
integer- or half-integer neighborhoods under explicitly stated bounds.
No discretization is performed at the encoding stage itself.

\subsection{Definition of the logarithmic coordinate}

For a fixed anchor scale $x_0$, we define
\begin{equation}
\Delta(x) \;\equiv\; \frac{\log(x/x_0)}{\log \lambda},
\label{eq:encoding_def}
\end{equation}
where $\lambda>1$ is a fixed scaling constant held constant across all scans in the paper series.
Equation~\eqref{eq:encoding_def} is a change of coordinates; it introduces no assumptions about
quantization or dynamics.

Two points are emphasized:
\begin{enumerate}
\item The encoding is continuous. Integer structure, when observed, emerges only after scanning and
comparison.
\item All dependence on physical units is confined to the choice of anchor $x_0$.
\end{enumerate}

\subsection{Invertibility and invariance}

The map $\mathcal{E}$ is invertible on its domain:
\begin{equation}
x \;=\; x_0\,\lambda^{\Delta(x)}.
\end{equation}
Consequently, no information is lost at the encoding stage.
Any failure or ambiguity observed in later sections is therefore attributable to the scan protocol or
the imposed bounds, not to the encoding itself.

Ratios of observables satisfy
\begin{equation}
\Delta(x_1)-\Delta(x_2) \;=\; \frac{\log(x_1/x_2)}{\log \lambda},
\end{equation}
which is independent of the anchor choice.
This invariance is exploited in later diagnostic tests but is not required for the definition of the map.

\subsection{Separation from fitting and interpretation}

The encoding map defined here is applied uniformly to all inputs prior to any fitting,
integer assignment, or hypothesis testing.
In particular:
\begin{itemize}
\item No rounding or snapping to integer values occurs at this stage.
\item No preference is assigned to any specific integer or lattice structure.
\item No interpretation is attached to $\Delta(x)$ beyond its role as a coordinate.
\end{itemize}

This strict separation ensures that the encoding layer cannot be tuned to improve downstream outcomes.
All degrees of freedom associated with scanning, matching, and evaluation are introduced explicitly and
independently in Section~\ref{sec:bounded_scan_protocol}.
