% ============================================================
% Paper VI.B section: results/interpretation bridge
% File: papers/sections/06b_results_summary.tex
% ============================================================

\section{Numerical mixing results and interpretation}
\label{sec:mixing_results_summary}

This section is a results-oriented bridge between the holonomy hypothesis and the formal verification narrative.
The numerical outputs themselves are externalized as a versioned artifact and are included verbatim in Section~\ref{sec:holonomy_mixing}.
Here we state only what is being tested and what constitutes success or failure.

\subsection{What is fixed, what is scanned}
Given fixed global-fit inputs $s_{12}, s_{23}, s_{13}$ for CKM or PMNS, we scan a Dirac CP phase
$\delta \in [0^\circ,360^\circ]$ on a dense grid and select the best match to a model-supplied holonomy angle $\theta_{\star}$
using a pre-registered matching rule (degree-space or sine-space). The Jarlskog invariant $J$ is then computed as a consistency check.

\subsection{What is reported and why it is verification-grade}
The repository script \texttt{code/verify\_mixing.py} prints all inputs and returns a deterministic best-fit phase $\delta$
along with the match score and $J$. It also writes a LaTeX-ready block to \texttt{shared/paperV\_mixing\_results.tex}, which is treated
as an externalized, versioned artifact. Under this workflow, the paper never depends on manual copy-paste of numeric results.

\subsection{Interpretation}
This verification step establishes that the scan-and-match protocol is implemented correctly and that a chosen $\theta_{\star}$ produces
a definite phase assignment and $J$ once the input sines are fixed. The substantive physics claim is that $\theta_{\star}$ is fixed by an
independent geometric mechanism and remains stable under updated global fits, scheme choices, and pre-registered matching rules.

\subsection{Falsifiability triggers}
The holonomy-phase program fails if (i) modest updates of global-fit inputs destabilize the inferred phase beyond stated tolerances,
(ii) the matching rule must be changed after inspecting outcomes, or (iii) the quark and lepton sectors cannot be made simultaneously consistent
with a single geometric prescription for $\theta_{\star}$ once that prescription is stated explicitly.
