\section{Predictions and test program}
\label{sec:predictions}

The framework developed in this paper does not assert a generative model.
Once its structural assumptions are fixed, however, it implies conditional
predictions that can be tested against future data.

These predictions should be read in a strict conditional sense: if the
logarithmic lattice organization reported here reflects a genuine regularity
of the fermion spectrum, then the statements below should hold within stated
tolerances.

\subsection{Mass-spectrum consistency}

Improved measurements of fermion masses, particularly in the light-quark and
neutrino sectors, should not disrupt the observed lattice alignment beyond
the residual bounds reported in Sec.~\ref{sec:results}.

A systematic drift away from lattice locations under refined data would
constitute evidence against the framework.

\subsection{Stability under updated inputs}

As experimental uncertainties shrink, best-fit integer assignments should
remain stable under the same anchoring and scan rules. Frequent reassignment
of integers under small input changes would indicate that the observed
structure is accidental rather than structural.

\subsection{Mixing-phase refinement}

In the lepton sector, improved determination of the Dirac CP phase should
remain consistent with the sign and magnitude constraints identified in
Sec.~\ref{sec:pmns}, subject to experimental uncertainty.

No claim is made regarding a precise numerical value for future phase
measurements, only their consistency with the verified framework.